---
title: "CMDA-4654  \n Group Excercise 2"
author: "Gavin Lopez, Hieu Ngo"
date: "3/31/2025"
output:
  pdf_document:
    highlight: haddock
keep_tex: no
number_sections: no
html_document:
  df_print: paged
geometry: margin = 0.5in
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
editor_options:
  chunk_output_type: console
documentclass: article
urlcolor: blue
---
  
<!-- The above is set to automatically compile to a .pdf file.   -->
<!-- It will only succeed if LaTeX is installed. -->


```{r setup, include=FALSE}
# This is the setup chunk
#  Here you can set global options for the entire document

library(knitr) # I recommend doing this here
library(ggplot2)
library(MASS)
library(class)
# Although you can call functions from a library using the following notation
#  without loading the entire library.
knitr::opts_chunk$set(echo = TRUE, 
                      comment = NA, # Required
                      fig.path = "./figures/",  # Store all figures here in relative path (make the folder first)
                      fig.align = "center",
                      fig.width = 7,
                      fig.height = 7,
                      message = FALSE, # Turn off load messages
                      warning = FALSE # Turn off warnings
                      )

```

\clearpage

```{r include=FALSE}
# You should not echo this chunk.
# include=FALSE does more than echo=FALSE, it actually does: echo=FALSE, results='hide', message=FALSE, warning=FALSE, fig.show='hide'

# You should set your working directory at the very beginning of your R Markdown file
# setwd("~/Dropbox/teaching/FA2020/CMDA_4654/homework/homework1/")

# In linux ~/ is shorthand for /home/username/
# You should type things out properly for your system
# Mac: /Users/username/Documents/CMDA4654/Lectures/Lecture_03/.../
# Windows: C:/Users/username/Documents/etc/Lecture/Lecture_03/.../


```

<!-- ---------------------------------------------------------------------------------------------------- -->
<!-- ---------------- Homework Problems start below these lines ----------------------------------------- -->
<!-- ---------------------------------------------------------------------------------------------------- -->


# Part 1

```{r}
# Your function will have the following inputs.
# 
# * x - a numeric input vector
# * y - a numeric response
#
# Note span and degree are shown with their default values. (Read about this in the description)
# * degree should be 1 or 2 only
# * span can be any value in interval (0, 1) non-inclusive.
#
# If show.plot = TRUE then you must show a plot of either the final fit

myloess <- function(x, y, span = 0.5, degree = 1, show.plot = TRUE) {
  
  N_total <- length(x)
  yhat <- numeric(N_total)
  
  # Capture variable names for axis labeling
  x_label <- deparse(substitute(x))
  y_label <- deparse(substitute(y))

  # Neighborhood size
  k <- ceiling(span * N_total)
  
  for (i in 1:N_total) {
    dists <- abs(x - x[i])
    
    neighbors <- order(dists)[1:k]
    x_local <- x[neighbors]
    y_local <- y[neighbors]
    
    D <- max(abs(x_local - x[i]))
    u <- abs(x_local - x[i]) / D
    w <- ifelse(u < 1, (1 - abs(u)^3)^3, 0)
    
    if (degree == 1) {
      X <- cbind(1, x_local)
      x_i_row <- c(1, x[i])
    } else if (degree == 2) {
      X <- cbind(1, x_local, x_local^2)
      x_i_row <- c(1, x[i], x[i]^2)
    }
    
    W <- diag(w)
    beta <- solve(t(X) %*% W %*% X) %*% (t(X) %*% W %*% y_local)
    
    yhat[i] <- x_i_row %*% beta
  }
  
  SSE <- sum((y - yhat)^2)
  MSE <- SSE / N_total
  
  df_plot <- data.frame(x = x, y = y, yhat = yhat)
  loessplot <- ggplot(df_plot, aes(x = x)) +
    geom_point(aes(y = y)) +
    geom_line(aes(y = yhat), color = "blue", size = 1) +
    labs(
      title = paste("LOESS - Degree:", degree, ", Span:", round(span, 2)),
      x = x_label,
      y = y_label
    )
  
  if (show.plot) {
    print(loessplot)
  }
  
  return(list(
    span = span,
    degree = degree,
    N_total = N_total,
    SSE = SSE,
    MSE = MSE,
    loessplot = loessplot
  ))
}

# Your function should return a named list containing the following:
# span: proportion of data used in each window (controls the bandwidth)
# degree: degree of polynomial
# N_total: total number of points in the data set
# SSE: Error Sum of Squares (Tells us how good of a fit we had).
# MSE: The Mean Squared Error for the Predictions
# loessplot: An object containing the ggplot so that we can see the plot later. 
#  We want this even if show.plot = FALSE
#  Note: you are NOT allowed to simply use stat_smooth() or geom_smooth() 
#         to have it automatically do LOESS.
#  You should use geom_line() or similar to plot your final the LOESS curve.

# Make sure you can access the objects properly using the $ notation.
```


## Problem 1

```{r}
load("C:/Users/gavin/OneDrive/Documents/CMDA 4654/Group Exercise 2/ozone.RData")
data("ozone")

# ggplot(ozone, aes(x = temperature, y = ozone)) + theme_bw() + geom_point()
```

### Section 1
```{r}

ggplot(ozone, aes(x = temperature, y = ozone)) +
  geom_point(color = "gray") +
  stat_smooth(method = "lm", 
              formula = y ~ poly(x, 1), 
              aes(color = "Degree 1"), se = FALSE) +
  stat_smooth(method = "lm", 
              formula = y ~ poly(x, 2), 
              aes(color = "Degree 2"), se = FALSE) +
  stat_smooth(method = "lm", 
              formula = y ~ poly(x, 3), 
              aes(color = "Degree 3"), se = FALSE) +
  stat_smooth(method = "lm", 
              formula = y ~ poly(x, 4), 
              aes(color = "Degree 4"), se = FALSE) +
  stat_smooth(method = "lm", 
              formula = y ~ poly(x, 5), 
              aes(color = "Degree 5"), se = FALSE) +
  stat_smooth(method = "lm", 
              formula = y ~ poly(x, 6), 
              aes(color = "Degree 6"), se = FALSE) +
  labs(title = "Polynomial Fits of Degree 1–6",
       color = "Polynomial Degree") +
  theme_minimal()
```
Polynomial 5 and 6 work the best. They are practically identical to one another, following the main curvature of data, smooth, and doesnt have any extra noise/fluctuations


### Section 2
```{r}
all_spans <- c()
all_degrees <- c()
all_MSEs <- c()
all_SSEs <- c()
# all_N <- c()
# Span sequence
spans <- seq(0.25, 0.75, by = 0.05)

# Loop through degrees and spans
for (d in c(1, 2)) {
  for (s in spans) {
    res <- myloess(x = ozone$temperature, y = ozone$ozone, span = s, degree = d, show.plot = FALSE)
    
    all_spans <- c(all_spans, s)
    all_degrees <- c(all_degrees, d)
    all_MSEs <- c(all_MSEs, res$MSE)
    all_SSEs <- c(all_SSEs, res$SSE)
    # all_N <- c(all_N, res$N_total)
  }
}
# Get index for each degree
deg1_index <- which(all_degrees == 1)
deg2_index <- which(all_degrees == 2)

# get top 3 indices with smallest MSE
top1_index <- deg1_index[order(all_MSEs[deg1_index])[1:3]]
top2_index <- deg2_index[order(all_MSEs[deg2_index])[1:3]]

# Plot top 3 for degree 1
for (i in top1_index) {
  s <- all_spans[i]
  fit <- myloess(x = ozone$temperature, y = ozone$ozone, span = s, degree = 1, show.plot = TRUE)
  fit$loessplot + ggtitle(paste("Degree = 1, Span =", s))
}

# Plot top 3 for degree 2
for (i in top2_index) {
  s <- all_spans[i]
  fit <- myloess(x = ozone$temperature, y = ozone$ozone, span = s, degree = 2, show.plot = TRUE)
  fit$loessplot + ggtitle(paste("Degree = 2, Span =", s))
}
results_table <- data.frame(
  # N_total = all_N,
  Span = all_spans,
  Degree = all_degrees,
  MSE = all_MSEs,
  SSE = all_SSEs
)

print(results_table)
```
The first two fits (especially span = 0.25) likely overfit the data. The model is reacting to minor fluctuations in the data rather than modeling the true underlying trend, hence a sharp peak at x = 80, and 84. At span = 0.35 looks like a better generalization, it's smoother, and follows the main structure.

### Section 3
```{r}
# LOESS comparison
loess_fit <- loess(ozone ~ temperature, data = ozone, span = 0.5, degree = 1)
ozone$fit_loess <- predict(loess_fit)

ggplot(ozone, aes(x = temperature, y = ozone)) +
  geom_point() +
  geom_smooth(method = "loess", se = F, span = 0.5, formula = y ~ x) +
  ggtitle("LOESS regression fit")

```
At low spans, myloess produces fits that are overfitting. The built in loess function might use a higher span, which naturally smooths things better. Span = 0.35 version begins to behave similarly to the built in one, implying it may be close to optimal.


## Problem 2

```{r}
data("mcycle")

# ggplot(mcycle, aes(x = times, y = accel)) + theme_bw() + geom_point()
```

## Section 1
```{r}

all_spans <- c()
all_degrees <- c()
all_MSEs <- c()
all_SSEs <- c()
all_N <- c()
# Span sequence
spans <- seq(0.25, 0.75, by = 0.05)

# Loop through degrees and spans
for (d in c(1, 2)) {
  for (s in spans) {
    res <- myloess(x = mcycle$times, y = mcycle$accel, span = s, degree = d, show.plot = FALSE)
    
    all_spans <- c(all_spans, s)
    all_degrees <- c(all_degrees, d)
    all_MSEs <- c(all_MSEs, res$MSE)
    all_SSEs <- c(all_SSEs, res$SSE)
    all_N <- c(all_N, res$N_total)
  }
}
# Get index for each degree
deg1_index <- which(all_degrees == 1)
deg2_index <- which(all_degrees == 2)

# get top 3 indices with smallest MSE
top1_index <- deg1_index[order(all_MSEs[deg1_index])[1:3]]
top2_index <- deg2_index[order(all_MSEs[deg2_index])[1:3]]

# Plot top 3 for degree 1
for (i in top1_index) {
  s <- all_spans[i]
  fit <- myloess(x = mcycle$times, y = mcycle$accel, span = s, degree = 1, show.plot = TRUE)
  fit$loessplot + ggtitle(paste("Degree = 1, Span =", s))
}

# Plot top 3 for degree 2
for (i in top2_index) {
  s <- all_spans[i]
  fit <- myloess(x = mcycle$times, y = mcycle$accel, span = s, degree = 2, show.plot = TRUE)
  fit$loessplot + ggtitle(paste("Degree = 2, Span =", s))
}
results_table <- data.frame(
  N_total = all_N,
  Span = all_spans,
  Degree = all_degrees,
  MSE = all_MSEs,
  SSE = all_SSEs
)

print(results_table)
```
The model that provides the best fit is degree 2 span .35. It effectively captures the structure of the data without reacting excessively and overfilling the data, suggesting it generalizes decently well.

## Section 2
```{r}
# LOESS comparison
loess_fit <- loess(times ~ accel, data = mcycle, span = 0.5, degree = 1)
mcycle$fit_loess <- predict(loess_fit)

ggplot(mcycle, aes(x = times, y = accel)) +
  geom_point() +
  geom_smooth(method = "loess", se = F, span = 0.5, formula = y ~ x) +
  ggtitle("LOESS regression fit")

```
The loess fit with degree 2 span .35 matches with the built in loess functions fit the best. It balances flexibility and smoothness, capturing the shape of the data without overfitting it.

# Part 2

# Problem 3

```{r}
mykNN <- function(train, test, y_train, y_test, k = 3, weighted = TRUE){
  
  # If the inputs are data frames, convert categorical predictors to dummy variables.
  if(is.data.frame(train)){
    train <- model.matrix(~ . - 1, data = train)
  }
  
  
  
  # Ensure test and train are matrices (if test is a single observation, convert it to a row matrix)
  if (is.null(dim(test))) {
    test <- matrix(test, nrow = 1)
  }
  if (is.null(dim(train))) {
    train <- matrix(train, nrow = 1)
  }
  # Standardize training data and apply the same scaling to test data.
  t_means <- colMeans(train)
  train_sds <- apply(train, 2, sd)
  train <- scale(train, center = t_means, scale = train_sds)
  test <- scale(test, center = t_means, scale = train_sds)

  
  n_test <- nrow(test)
  
  
  # For classification, use a character vector,
  # for regression, use a numeric vector.
  classification <- is.factor(y_train)
  if(classification){
    yhat <- vector("character", n_test)
  } else {
    yhat <- numeric(n_test)
  }
  
  # Loop over each test observation.
  for(i in 1:n_test){

    test_point <- test[i, ]
    # Compute Euclidean distances 
    distances <- sqrt(rowSums((train - matrix(test_point, 
                                                nrow = nrow(train), 
                                                ncol = ncol(train), 
                                                byrow = TRUE))^2))
    
    # Identify the indices of the k nearest neighbors.
    n_idx <- order(distances)[1:k]
    n_distances <- distances[n_idx]
    n_responses <- y_train[n_idx]
    
    # Classification: y_train is a factor.
    if(classification){
      if(weighted){
        # Handle any zero distances by directly using those neighbors.
        if(any(n_distances == 0)){
          exact_matches <- n_responses[n_distances == 0]
          prediction <- names(which.max(table(exact_matches)))
        } else {
          # Compute weights as inverse distances.
          weights <- 1 / n_distances
          # Sum weights for each class.
          class_weights <- tapply(weights, n_responses, sum)
          prediction <- names(which.max(class_weights))
        }
      } else {
        # Unweighted: simple majority vote.
        prediction <- names(which.max(table(n_responses)))
      }
      yhat[i] <- prediction
      
    } else {
      # Regression option
      if(weighted){
        if(any(n_distances == 0)){

          prediction <- mean(n_responses[n_distances == 0])
        } else {
          weights <- 1 / n_distances
         
          weights <- weights / sum(weights)
          prediction <- sum(weights * n_responses)
        }
      } else {
  
        prediction <- mean(n_responses)
      }
      yhat[i] <- prediction
    }
  }
  
  # Return the output for each type
  if(classification){
    # Convert predictions to factor with same levels as y_train.
    yhat <- factor(yhat, levels = levels(y_train))
    # Calculate accuracy and error rate.
    accuracy <- sum(yhat == y_test) / length(y_test)
    error_rate <- 1 - accuracy
    # Create confusion matrix.
    confusion_mat <- table(Predicted = yhat, Actual = y_test)
    
    return(list(yhat = yhat,
                accuracy = accuracy,
                error_rate = error_rate,
                confusion_matrix = confusion_mat,
                k = k))
  } else {
    # For regression, compute residuals and errors.
    residuals <- y_test - yhat
    SSE <- sum(residuals^2)
    MSE <- SSE / length(y_test)
    
    return(list(yhat = yhat,
                residuals = residuals,
                SSE = SSE,
                n_test = length(y_test),
                MSE = MSE,
                k = k))
  }
}
```

# Prepare the data set
```{r}
# Some pre-processing
library(ISLR)
# Remove the name of the car model and change the origin to categorical with actual name
Auto_new <- Auto[, -9]
# Lookup table
newOrigin <- c("USA", "European", "Japanese")
Auto_new$origin <- factor(newOrigin[Auto_new$origin], newOrigin)

# Look at the first 6 observations to see the final version
head(Auto_new)
```



```{r}
# Split data into 70% training and 30% testing
set.seed(123)  # for reproducibility
n <- nrow(Auto_new)
train_indices <- sample(1:n, size = floor(0.7 * n))
train_data <- Auto_new[train_indices, ]
test_data  <- Auto_new[-train_indices, ]

# Separate predictors and response.
# We use all features (mpg, cylinders, displacement, horsepower, weight, acceleration, year) 
# to predict origin.
pred_cols <- setdiff(names(Auto_new), "origin")
train_pred <- train_data[, pred_cols]
test_pred  <- test_data[, pred_cols]
train_response <- train_data$origin
test_response  <- test_data$origin


# We'll test several k values.
k_vals <- c(1, 3, 5, 7, 9, 12, 15, 20)

# Create result data frames for unweighted (regular) and weighted (dnkNN) methods.
results_unweighted <- data.frame(k = k_vals, accuracy = NA)
results_weighted   <- data.frame(k = k_vals, accuracy = NA)

for(i in seq_along(k_vals)){
  k_val <- k_vals[i]
  
  # Regular (unweighted) kNN
  unweighted <- mykNN(train = train_pred, test = test_pred, 
                   y_train = train_response, y_test = test_response, 
                   k = k_val, weighted = FALSE)
  results_unweighted$accuracy[i] <- unweighted$accuracy
  
  # Distance weighted kNN
  weighted <- mykNN(train = train_pred, test = test_pred, 
                 y_train = train_response, y_test = test_response, 
                 k = k_val, weighted = TRUE)
  results_weighted$accuracy[i] <- weighted$accuracy
}


kable(results_unweighted, caption = "Accuracy for Regular kNN")
kable(results_weighted, caption = "Accuracy for Distance Weighted kNN")

# Plot accuracy vs k for both methods
results_unweighted$Method <- "Regular"
results_weighted$Method   <- "Weighted"
results_all <- rbind(results_unweighted, results_weighted)

ggplot(results_all, aes(x = k, y = accuracy, color = Method)) +
  geom_point(size = 3) +
  
  labs(title = "Accuracy vs. Number of Neighbors (k)",
       x = "Number of Neighbors (k)",
       y = "Accuracy") +
  theme_minimal()

# Determine best for each method:
best_k_unweighted <- results_unweighted$k[which.max(results_unweighted$accuracy)]
best_acc_unweighted <- max(results_unweighted$accuracy)
best_k_weighted <- results_weighted$k[which.max(results_weighted$accuracy)]
best_acc_weighted <- max(results_weighted$accuracy)

cat("Best k for Regular kNN: ", best_k_unweighted, "with accuracy", best_acc_unweighted, "\n")
cat("Best k for Weighted kNN: ", best_k_weighted, "with accuracy", best_acc_weighted, "\n")

# Show final confusion matrix for the best k for each method:
final_unw <- mykNN(train = train_pred, test = test_pred, 
                   y_train = train_response, y_test = test_response, 
                   k = best_k_unweighted, weighted = FALSE)
final_w <- mykNN(train = train_pred, test = test_pred, 
                 y_train = train_response, y_test = test_response, 
                 k = best_k_weighted, weighted = TRUE)

cat("Confusion Matrix for Regular kNN (k =", best_k_unweighted, "):\n")
print(final_unw$confusion_matrix)
cat("Accuracy:", final_unw$accuracy, "\n\n")

cat("Confusion Matrix for Distance Weighted kNN (k =", best_k_weighted, "):\n")
print(final_w$confusion_matrix)
cat("Accuracy:", final_w$accuracy, "\n\n")

# Plot MPG vs. Weight for k = 5 and k = 10

k_ <- mykNN(train = train_pred, test = test_pred, 
               y_train = train_response, y_test = test_response, 
               k = 5, weighted = TRUE)
k_10 <- mykNN(train = train_pred, test = test_pred, 
                y_train = train_response, y_test = test_response, 
                k = 10, weighted = TRUE)

# Prepare data for plotting:

train_plot <- train_data[, c("mpg", "weight", "origin")]
train_plot$set <- "Train"

test_plot <- test_data[, c("mpg", "weight", "origin")]
test_plot$set <- "Test"

# Plot for k = 5
p1 <- ggplot() +
  geom_point(data = train_plot, aes(x = weight, y = mpg, color = origin),
             shape = 16, alpha = 0.5, size = 3) +
  geom_point(data = test_plot, aes(x = weight, y = mpg, color = origin),
             shape = 18, size = 4) +
  labs(title = "MPG vs. Weight (k = 5, Weighted kNN)",
       x = "Weight", y = "MPG") +
  theme_minimal()
print(p1)

# Plot for k = 10
p2 <- ggplot() +
  geom_point(data = train_plot, aes(x = weight, y = mpg, color = origin),
             shape = 16, alpha = 0.5, size = 3) +
  geom_point(data = test_plot, aes(x = weight, y = mpg, color = origin),
             shape = 18, size = 4) +
  labs(title = "MPG vs. Weight (k = 10, Weighted kNN)",
       x = "Weight", y = "MPG") +
  theme_minimal()
print(p2)

```

# Check if the my function is different from the built in function
```{r}



# Use custom Knn function for unweighted
my_knn_result <- mykNN(train = train_pred, test = test_pred, 
                       y_train = train_response, y_test = test_response, 
                       k = best_k_unweighted, weighted = FALSE)

# Use the built-in knn() function for unweighted kNN.
builtin_knn <- knn(train = train_pred, test = test_pred, 
                        cl = train_response, k = best_k_unweighted)

# Compare predictions by creating a confusion table.
comparison_table <- table(Custom = my_knn_result$yhat, BuiltIn = builtin_knn)
print(comparison_table)

# Calculate accuracy for both methods.
accuracy_builtin <- mean(builtin_knn == test_response)
accuracy_custom <- my_knn_result$accuracy

cat("Built-in knn accuracy:", accuracy_builtin, "\n")
cat("Custom mykNN accuracy:", accuracy_custom, "\n")
```

# Problem 4
## Part a
```{r}
# load("C:/Users/gavin/OneDrive/Documents/CMDA 4654/Group Exercise 2/ozone.RData")
# data("ozone")
# ggplot(ozone, aes(x = temperature, y = ozone)) + theme_bw() + geom_point()
```

```{r}
# Split the data set
set.seed(123)  # For reproducibility
n_total <- nrow(ozone)
train_idx <- sample(1:n_total, 70)
train_ozone <- ozone[train_idx, ]
test_ozone  <- ozone[-train_idx, ]


# For the regression fit, we'll use only the predictor 'temperature'.
# We also standardize the predictor based on the training set.
train_temp <- data.frame(temperature = train_ozone$temperature)
test_temp  <- data.frame(temperature = test_ozone$temperature)

# Define k values to try
k_set <- c(1, 3, 5, 10, 20)

# Prepare a data frame to store the MSE results.
results<- data.frame(k = k_set, MSE = NA)

# Loop over each k value and obtain predictions using dwkNN.
for(i in seq_along(k_set)){
  k_val <- k_set[i]
  fit <- mykNN(train = train_temp,
               test  = test_temp,
               y_train = train_ozone$ozone,
               y_test  = test_ozone$ozone,
               k = k_val,
               weighted = TRUE)
  results_all$MSE[i] <- fit$MSE
}

# Display the results table 
kable(results_all, caption = "Test MSE for dwkNN (ozone ~ temperature) for various k")

# Choose the best k for plotting the regression line.
best_k_a <- results_all$k[which.min(results_all$MSE)]
cat("Best k in part (a):", best_k_a, "with MSE =", min(results_all$MSE), "\n")

# Create a grid of temperature values for plotting the regression line.
temp_grid <- data.frame(temperature = seq(min(train_temp$temperature),
                                               max(train_temp$temperature),
                                               length.out = 100))

# Obtain predictions on the grid using the best k.
grid_fit <- mykNN(train = train_temp,
                  test = temp_grid,
                  y_train = train_ozone$ozone,
                  y_test = NA,  
                  k = best_k_a,
                  weighted = TRUE)
grid_pred <- grid_fit$yhat

# Ploting


plot_a <- ggplot() +
  geom_point(data = train_ozone, aes(x = temperature, y = ozone), 
             color = "black", size = 3) +
  geom_point(data = test_ozone, aes(x = temperature, y = ozone), 
             color = "blue", size = 3) +
  geom_line(data = data.frame(temperature = temp_grid$temperature,
                              ozone = grid_pred),
            aes(x = temperature, y = ozone),
            color = "red", size = 1) +
  labs(title = paste("dwkNN Regression (ozone ~ temperature) with k =", best_k_a),
       x = "Temperature",
       y = "Ozone") +
  theme_minimal()
print(plot_a)

```
### Comment on the results
As we could see from the results table, k = 3 gives the lowest MSE, while k = 1 seems to over fit the data while k = 5, and k = 10 over smooth the data. The train data and the test data show that the data have a strong overall upward trend but when the temperature is high there is a considerable fluctuated factors. In short, the MSE is still relatively large so it could not alone explain the variability ozone.

## Part b
```{r}
# Setup predictors variable
pred_cols <- setdiff(names(ozone), "ozone")
train_pred <- train_ozone[, pred_cols]
test_pred  <- test_ozone[, pred_cols]




k_set <- 1:20
results <- data.frame(k = k_set, MSE = NA)

for(k_val in k_set){
  fit_line <- mykNN(train = train_pred,
                 test = test_pred,
                 y_train = train_ozone$ozone,
                 y_test = test_ozone$ozone,
                 k = k_val,
                 weighted = TRUE)
  results$MSE[results$k == k_val] <- fit_line$MSE
}

# Display the results table 
kable(results, caption = "Test MSE for dwkNN (ozone ~ all predictors) for various k")

# Plot MSE versus k for part (b)
plot <- ggplot(results, aes(x = k, y = MSE)) +
  geom_point(size = 3) +
  geom_line() +
  labs(title = "Test MSE vs. k (dwkNN with all predictors)",
       x = "Number of Neighbors (k)",
       y = "Test MSE") +
  theme_minimal()
print(plot)
```
### Comment on the results
In this case, when we increased k from 1 to 20, the prediction error kept dropping and then flattened out, meaning that using around 20 neighbors gave us the best stable prediction. It suggests that for our data, looking at a broader group (around 20 neighbors) is beneficial, and we didn't see the error getting worse within the range we tested.
Additionally we could use a broader range of case for a more precise prediction.
