---
title: "CMDA-4654  \n Group Excercise 2"
author: "Gavin Lopez, Hieu"
date: "3/31/2025"
output:
  pdf_document:
    highlight: haddock
keep_tex: no
number_sections: no
html_document:
  df_print: paged
geometry: margin = 0.5in
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
editor_options:
  chunk_output_type: console
documentclass: article
urlcolor: blue
---
  
<!-- The above is set to automatically compile to a .pdf file.   -->
<!-- It will only succeed if LaTeX is installed. -->


```{r setup, include=FALSE}
# This is the setup chunk
#  Here you can set global options for the entire document

library(knitr) # I recommend doing this here
library(ggplot2)
library(MASS)
# Although you can call functions from a library using the following notation
#  without loading the entire library.
knitr::opts_chunk$set(echo = TRUE, 
                      comment = NA, # Required
                      fig.path = "./figures/",  # Store all figures here in relative path (make the folder first)
                      fig.align = "center",
                      fig.width = 7,
                      fig.height = 7,
                      message = FALSE, # Turn off load messages
                      warning = FALSE # Turn off warnings
                      )

```

\clearpage

```{r include=FALSE}
# You should not echo this chunk.
# include=FALSE does more than echo=FALSE, it actually does: echo=FALSE, results='hide', message=FALSE, warning=FALSE, fig.show='hide'

# You should set your working directory at the very beginning of your R Markdown file
# setwd("~/Dropbox/teaching/FA2020/CMDA_4654/homework/homework1/")

# In linux ~/ is shorthand for /home/username/
# You should type things out properly for your system
# Mac: /Users/username/Documents/CMDA4654/Lectures/Lecture_03/.../
# Windows: C:/Users/username/Documents/etc/Lecture/Lecture_03/.../


```

<!-- ---------------------------------------------------------------------------------------------------- -->
<!-- ---------------- Homework Problems start below these lines ----------------------------------------- -->
<!-- ---------------------------------------------------------------------------------------------------- -->


# Part 1

```{r}
# Your function will have the following inputs.
# 
# * x - a numeric input vector
# * y - a numeric response
#
# Note span and degree are shown with their default values. (Read about this in the description)
# * degree should be 1 or 2 only
# * span can be any value in interval (0, 1) non-inclusive.
#
# If show.plot = TRUE then you must show a plot of either the final fit

myloess <- function(x, y, span = 0.5, degree = 1, show.plot = TRUE) {
  
  N_total <- length(x)
  yhat <- numeric(N_total)
  
  # Capture variable names for axis labeling
  x_label <- deparse(substitute(x))
  y_label <- deparse(substitute(y))

  # Neighborhood size
  k <- ceiling(span * N_total)
  
  for (i in 1:N_total) {
    dists <- abs(x - x[i])
    
    neighbors <- order(dists)[1:k]
    x_local <- x[neighbors]
    y_local <- y[neighbors]
    
    D <- max(abs(x_local - x[i]))
    u <- abs(x_local - x[i]) / D
    w <- ifelse(u < 1, (1 - abs(u)^3)^3, 0)
    
    if (degree == 1) {
      X <- cbind(1, x_local)
      x_i_row <- c(1, x[i])
    } else if (degree == 2) {
      X <- cbind(1, x_local, x_local^2)
      x_i_row <- c(1, x[i], x[i]^2)
    }
    
    W <- diag(w)
    beta <- solve(t(X) %*% W %*% X) %*% (t(X) %*% W %*% y_local)
    
    yhat[i] <- x_i_row %*% beta
  }
  
  SSE <- sum((y - yhat)^2)
  MSE <- SSE / N_total
  
  df_plot <- data.frame(x = x, y = y, yhat = yhat)
  loessplot <- ggplot(df_plot, aes(x = x)) +
    geom_point(aes(y = y)) +
    geom_line(aes(y = yhat), color = "blue", size = 1) +
    labs(
      title = paste("LOESS - Degree:", degree, ", Span:", round(span, 2)),
      x = x_label,
      y = y_label
    )
  
  if (show.plot) {
    print(loessplot)
  }
  
  return(list(
    span = span,
    degree = degree,
    N_total = N_total,
    SSE = SSE,
    MSE = MSE,
    loessplot = loessplot
  ))
}

# Your function should return a named list containing the following:
# span: proportion of data used in each window (controls the bandwidth)
# degree: degree of polynomial
# N_total: total number of points in the data set
# SSE: Error Sum of Squares (Tells us how good of a fit we had).
# MSE: The Mean Squared Error for the Predictions
# loessplot: An object containing the ggplot so that we can see the plot later. 
#  We want this even if show.plot = FALSE
#  Note: you are NOT allowed to simply use stat_smooth() or geom_smooth() 
#         to have it automatically do LOESS.
#  You should use geom_line() or similar to plot your final the LOESS curve.

# Make sure you can access the objects properly using the $ notation.
```


## Problem 1

```{r}
load("C:/Users/gavin/OneDrive/Documents/CMDA 4654/Group Exercise 2/ozone.RData")
# data("ozone")

# ggplot(ozone, aes(x = temperature, y = ozone)) + theme_bw() + geom_point()
```

### Section 1
```{r}

ggplot(ozone, aes(x = temperature, y = ozone)) +
  geom_point(color = "gray") +
  stat_smooth(method = "lm", 
              formula = y ~ poly(x, 1), 
              aes(color = "Degree 1"), se = FALSE) +
  stat_smooth(method = "lm", 
              formula = y ~ poly(x, 2), 
              aes(color = "Degree 2"), se = FALSE) +
  stat_smooth(method = "lm", 
              formula = y ~ poly(x, 3), 
              aes(color = "Degree 3"), se = FALSE) +
  stat_smooth(method = "lm", 
              formula = y ~ poly(x, 4), 
              aes(color = "Degree 4"), se = FALSE) +
  stat_smooth(method = "lm", 
              formula = y ~ poly(x, 5), 
              aes(color = "Degree 5"), se = FALSE) +
  stat_smooth(method = "lm", 
              formula = y ~ poly(x, 6), 
              aes(color = "Degree 6"), se = FALSE) +
  labs(title = "Polynomial Fits of Degree 1–6",
       color = "Polynomial Degree") +
  theme_minimal()
```
Polynomial 5 and 6 work the best. They are practically identical to one another, following the main curvature of data, smooth, and doesnt have any extra noise/fluctuations


### Section 2
```{r}
all_spans <- c()
all_degrees <- c()
all_MSEs <- c()
all_SSEs <- c()
# all_N <- c()
# Span sequence
spans <- seq(0.25, 0.75, by = 0.05)

# Loop through degrees and spans
for (d in c(1, 2)) {
  for (s in spans) {
    res <- myloess(x = ozone$temperature, y = ozone$ozone, span = s, degree = d, show.plot = FALSE)
    
    all_spans <- c(all_spans, s)
    all_degrees <- c(all_degrees, d)
    all_MSEs <- c(all_MSEs, res$MSE)
    all_SSEs <- c(all_SSEs, res$SSE)
    # all_N <- c(all_N, res$N_total)
  }
}
# Get index for each degree
deg1_index <- which(all_degrees == 1)
deg2_index <- which(all_degrees == 2)

# get top 3 indices with smallest MSE
top1_index <- deg1_index[order(all_MSEs[deg1_index])[1:3]]
top2_index <- deg2_index[order(all_MSEs[deg2_index])[1:3]]

# Plot top 3 for degree 1
for (i in top1_index) {
  s <- all_spans[i]
  fit <- myloess(x = ozone$temperature, y = ozone$ozone, span = s, degree = 1, show.plot = TRUE)
  fit$loessplot + ggtitle(paste("Degree = 1, Span =", s))
}

# Plot top 3 for degree 2
for (i in top2_index) {
  s <- all_spans[i]
  fit <- myloess(x = ozone$temperature, y = ozone$ozone, span = s, degree = 2, show.plot = TRUE)
  fit$loessplot + ggtitle(paste("Degree = 2, Span =", s))
}
results_table <- data.frame(
  # N_total = all_N,
  Span = all_spans,
  Degree = all_degrees,
  MSE = all_MSEs,
  SSE = all_SSEs
)

print(results_table)
```
The first two fits (especially span = 0.25) likely overfit the data. The model is reacting to minor fluctuations in the data rather than modeling the true underlying trend, hence a sharp peak at x = 80, and 84. At span = 0.35 looks like a better generalization, it's smoother, and follows the main structure.

### Section 3
```{r}
# LOESS comparison
loess_fit <- loess(ozone ~ temperature, data = ozone, span = 0.5, degree = 1)
ozone$fit_loess <- predict(loess_fit)

ggplot(ozone, aes(x = temperature, y = ozone)) +
  geom_point() +
  geom_smooth(method = "loess", se = F, span = 0.5, formula = y ~ x) +
  ggtitle("LOESS regression fit")

```
At low spans, myloess produces fits that are overfitting. The built in loess function might use a higher span, which naturally smooths things better. Span = 0.35 version begins to behave similarly to the built in one, implying it may be close to optimal.


## Problem 2

```{r}
data("mcycle")

# ggplot(mcycle, aes(x = times, y = accel)) + theme_bw() + geom_point()
```

## Section 1
```{r}

all_spans <- c()
all_degrees <- c()
all_MSEs <- c()
all_SSEs <- c()
all_N <- c()
# Span sequence
spans <- seq(0.25, 0.75, by = 0.05)

# Loop through degrees and spans
for (d in c(1, 2)) {
  for (s in spans) {
    res <- myloess(x = mcycle$times, y = mcycle$accel, span = s, degree = d, show.plot = FALSE)
    
    all_spans <- c(all_spans, s)
    all_degrees <- c(all_degrees, d)
    all_MSEs <- c(all_MSEs, res$MSE)
    all_SSEs <- c(all_SSEs, res$SSE)
    all_N <- c(all_N, res$N_total)
  }
}
# Get index for each degree
deg1_index <- which(all_degrees == 1)
deg2_index <- which(all_degrees == 2)

# get top 3 indices with smallest MSE
top1_index <- deg1_index[order(all_MSEs[deg1_index])[1:3]]
top2_index <- deg2_index[order(all_MSEs[deg2_index])[1:3]]

# Plot top 3 for degree 1
for (i in top1_index) {
  s <- all_spans[i]
  fit <- myloess(x = mcycle$times, y = mcycle$accel, span = s, degree = 1, show.plot = TRUE)
  fit$loessplot + ggtitle(paste("Degree = 1, Span =", s))
}

# Plot top 3 for degree 2
for (i in top2_index) {
  s <- all_spans[i]
  fit <- myloess(x = mcycle$times, y = mcycle$accel, span = s, degree = 2, show.plot = TRUE)
  fit$loessplot + ggtitle(paste("Degree = 2, Span =", s))
}
results_table <- data.frame(
  N_total = all_N,
  Span = all_spans,
  Degree = all_degrees,
  MSE = all_MSEs,
  SSE = all_SSEs
)

print(results_table)
```
The model that provides the best fit is degree 2 span .35. It effectively captures the structure of the data without reacting excessively and overfilling the data, suggesting it generalizes decently well.

## Section 2
```{r}
# LOESS comparison
loess_fit <- loess(times ~ accel, data = mcycle, span = 0.5, degree = 1)
mcycle$fit_loess <- predict(loess_fit)

ggplot(mcycle, aes(x = times, y = accel)) +
  geom_point() +
  geom_smooth(method = "loess", se = F, span = 0.5, formula = y ~ x) +
  ggtitle("LOESS regression fit")

```
The loess fit with degree 2 span .35 matches with the built in loess functions fit the best. It balances flexibility and smoothness, capturing the shape of the data without overfitting it.

# Part 2


